\documentclass[10pt,letterpaper]{report}

\usepackage{fontspec}
\setmainfont{GTZirkon}[
    Path = fonts/ ,
    UprightFont = *-Book,
    BoldFont = *-Bold,
    ItalicFont = *-Italic
]

%\usepackage[T1]{fontenc} % output T1 font encoding (8-bit) for accented characters as single glyph
\usepackage[strict,autostyle]{csquotes} % smart and nestable quote marks
\usepackage[USenglish]{babel} % regionalize hyphens, quote marks, etc automatically
\usepackage{microtype}% improve text appearance with kerning, etc
\usepackage{datetime} % enable formatting of date output
\usepackage{tabto}    % make nice tabbing
\usepackage{hyperref} % enable hyperlinks and pdf metadata
\usepackage{geometry} % manually set page margins
\usepackage{enumitem} % enumerate with [resume] option
\usepackage{titlesec} % allow custom section fonts
\usepackage{setspace} % custom line spacing
\usepackage{fancyhdr}
\usepackage{lastpage}

% what is your name?
\newcommand{\myname}{{Matt Franchi}}

% how far to tab for list items with left-aligned date: different fonts need different widths
\newcommand{\listtabwidth}{1.7cm}

% define font to use as document's title
\newcommand{\namefont}[1]{{\normalfont\bfseries\Huge{#1}}}

% set section heading fonts and before/after spacing
\titleformat{\section}{\lsstyle\bfseries\uppercase}{}{}{}{}
\titlespacing{\section}{0pt}{20pt plus 4pt minus 4pt}{6pt plus 2pt minus 2pt}

% set subsection heading fonts and before/after spacing
\titleformat{\subsection}{\lsstyle\bfseries}{}{}{}{}
\titlespacing{\subsection}{0pt}{10pt plus 4pt minus 4pt}{4pt plus 2pt minus 2pt}

% set page margins (tighter for compact layout)
\geometry{body={6.5in, 9.5in},
    left=1.0in,
    top=0.75in}

% prevent paragraph indentation
\setlength\parindent{0em}

% set line spacing
\setstretch{1}

% define space between list items
\newcommand{\listitemspace}{0.15em}

% make unordered lists without bullets and use compact spacing
\renewenvironment{itemize}
{\begin{list}{}{\setlength{\leftmargin}{0em}
                \setlength{\parskip}{0em}
                \setlength{\itemsep}{\listitemspace}
                \setlength{\parsep}{\listitemspace}}}
{\end{list}}

% make tabbed lists so content is left-aligned next to years
\TabPositions{\listtabwidth}
\newlist{tablist}{description}{3}
\setlist[tablist]{leftmargin=\listtabwidth,
    labelindent=0em,
    topsep=0em,
    partopsep=0em,
    itemsep=\listitemspace,
    parsep=\listitemspace,
    font=\normalfont}

% print only the month and year when using \today
\newdateformat{monthyeardate}{\monthname[\THEMONTH] \THEYEAR}

% define hyperlink appearance and metadata for pdf properties
\hypersetup{
    colorlinks  = true,
    urlcolor    = {rgb}{0.0, 0.0, 0.5},
    citecolor   = black,
    linkcolor   = black,
    pdfauthor   = {\myname},
    pdfkeywords = {computer science, urban visual analytics, computer vision, machine learning, responsible AI, PhD},
    pdftitle    = {\myname: Curriculum Vitae},
    pdfsubject  = {Curriculum Vitae},
    pdfpagemode = UseNone
}

\begin{document}
    \pagestyle{fancy}
    \fancyhf{}
    \renewcommand{\headrulewidth}{0pt}
    \fancyfoot[C]{\small \thepage{} of \pageref{LastPage}}
    \raggedright{}

    % display your name as the document title
    \namefont{\myname}

    % affiliation and contact info blocks
    \vspace{1em}
    \begin{minipage}[t]{0.6\textwidth}
         Cornell University, Cornell Tech \\ 
         Urban Tech Hub, \href{https://irl.tech.cornell.edu}{Interaction Research Lab (IRL)},\\ \href{https://dli.tech.cornell.edu}{Digital Life Initiative (DLI)}
    \end{minipage}
    \begin{minipage}[t]{0.39\textwidth}
        \flushright{}
        \href{mailto:howdy@mfranchi.net}{howdy@mfranchi.net} \\
        \href{https://mfranchi.net}{mfranchi.net} \\ 
        New York, New York
    \end{minipage}


    \section*{Education}

    \begin{tabular}{r| l l}
    Ph.D. & Computer Science, Cornell University & 2022--2028 (expected) \\
    M.S. & Computer Science, Cornell University & 2022--2024 \\
    B.S.H. & Computer Science, Clemson University & 2019--2021 \\
    \end{tabular}

    \section*{Research Interests}
    Urban visual analytics, interactive geospatial data visualization, and privacy-preserving AI inference in public settings

    \section*{Skills}

    Python, vLLM, Ray, Hydra; computer vision (CNNs, VLMs/MLLMs); Bayesian modeling, statistical ML; geospatial data science, cartography, data visualization; HPC, responsible AI

    \section*{Selected Publications}

    \begin{tablist}

        \item[2025] \tab{}Kenshikimyo Terao, Ilan Mandel, \textbf{Matt Franchi}, Chishang Mario Yang, Mark Colley, and Wendy Ju. ``Evaluating Interfaces for Non-Driving Related Tasks While Operating an E-Scooter.'' AutomotiveUI '25.

        \item[2025] \tab{}\textbf{Matt Franchi}, Nikhil Garg, Wendy Ju, and Emma Pierson. ``Bayesian Modeling of Zero-Shot Classifications for Urban Flood Detection.'' Under revision at Nature Communications. \href{https://arxiv.org/abs/2503.14754}{arXiv:2503.14754}.

        \item[2025] \tab{}\textbf{Matt Franchi}, Hauke Sandhaus, Madiha Zahrah Choksi, Severin Engelmann, Wendy Ju, and Helen Nissenbaum. ``Privacy of Groups in Dense Street Imagery.'' FAccT '25.

        \item[2025] \tab{}Dorin Shapira, \textbf{Matt Franchi}, and Wendy Ju. ``Fingerprinting New York City's Scaffolding Problem with Longitudinal Dashcam Data.'' CUPUM '25.

        \item[2025] \tab{}\textbf{Matt Franchi}, Maria-Teresa Parreira, Frank Bu, and Wendy Ju. ``The Robotability Score: Enabling Harmonious Robot Navigation on Urban Streets.'' CHI '25.

        \item[2024] \tab{}\textbf{Matt Franchi}, Debargha Dey, and Wendy Ju. ``Towards Instrumented Fingerprinting of Urban Traffic: A Novel Methodology using Distributed Mobile Point-of-View Cameras.'' AutomotiveUI '24. \textbf{Best Paper Honorable Mention.}

        \item[2023] \tab{}\textbf{Matt Franchi}, J.D. Zamfirescu-Pereira, Wendy Ju, and Emma Pierson. ``Detecting Disparities in Police Deployments Using Dashcam Data.'' FAccT '23.

    \end{tablist}

    \section*{Research Experience}

    \begin{tablist}
        \item[2026] \tab{}Graduate Research Assistant, Cornell Tech, with Dr. Helen Nissenbaum
        \item[2024] \tab{}Graduate Research Assistant, Cornell Tech, with Dr. Emma Pierson
        \item[2022--23] \tab{}Research Assistant, Cornell Tech, with Dr. Wendy Ju and Dr. Emma Pierson
        \item[2021] \tab{}Research Assistant (REU), Clemson University, with Dr. Amy Apon and BMW IT Research Center
    \end{tablist}

    \section*{Industry Experience}

    \begin{tablist}
        \item[2025] \tab{}PiTech Fellow, Design Trust for Public Space, New York, NY
        \item[2024--25] \tab{}Research Fellow, Hayden AI, San Francisco, CA
        \item[2021--22] \tab{}Software Engineer, High Side Technology, Charleston, SC
    \end{tablist}

    \section*{Selected Talks}

    \begin{tablist}
        \item[2025] \tab{}``Privacy of Groups in Dense Street Imagery.'' Digital Life Initiative Seminar, New York, NY.
        \item[2024] \tab{}``Detecting Urban Floods from Dashcam Data with Vision Language Models.'' Urban Tech Summit, New York, NY.
        \item[2024] \tab{}``Novel Approaches to Studying the Law Enforcement Investigatory Process.'' Association for Psychological Science (APS) Annual Convention.
    \end{tablist}

    \section*{Writing \& Media}

    \begin{tablist}
        \item[2026] \tab{}``How dashcams revealed 10\% of sidewalk sheds are illegal.'' Michael Samuelian and \textbf{Matt Franchi}. \href{https://nypost.com/2026/02/13/opinion/how-to-shed-those-ugly-sheds-and-see-paradise-by-the-dashboard-camera/}{New York Post} (op-ed).
        \item[2025] \tab{}``Digital Eyes on the Street.'' \href{https://dli.tech.cornell.edu/post/digital-eyes-on-the-street}{Digital Life Initiative}.
        \item[2025] \tab{}``Sensing AI Incidents \& Risks from Global News.'' \href{https://mfranchi.net/posts/uair-brief/}{mfranchi.net}.
        \item[2025] \tab{}``'Robotability Score' Ranks NYC Streets for Robot Deployment.'' \href{https://news.cornell.edu/stories/2025/04/robotability-score-ranks-nyc-streets-future-robot-deployment}{Cornell Chronicle}, ACM TechNews.
        \item[2024] \tab{}``Think N.Y.C.'s Roads Are Crowded? Good Luck on the Sidewalks.'' \href{https://www.nytimes.com/2024/07/29/nyregion/street-wars-crowded-sidewalks-times-square.html}{The New York Times}.
        \item[2024] \tab{}``New York City is covered in illegal scaffolding.'' \href{https://www.economist.com/science-and-technology/2024/03/13/new-york-city-is-covered-in-illegal-scaffolding}{The Economist}.
        \item[2023] \tab{}``The NYPD doesn't report where it deploys police. So scientists used AI, dashcams to find out.'' \href{https://gothamist.com/news/nypd-does-not-report-where-it-deploys-police-scientists-used-ai-dashcams-to-find-out}{Gothamist}.
    \end{tablist}

    \section*{Awards}

    \begin{tablist}
        \item[2025] \tab{}Siegel PiTech PhD Impact Fellowship, Design Trust for Public Space
        \item[2024] \tab{}Best Paper Honorable Mention, ACM AutomotiveUI
        \item[2024] \tab{}Digital Life Initiative (DLI) Doctoral Fellowship
        \item[2022] \tab{}Cornell Dean's Excellence Fellowship
        \item[2021] \tab{}Clemson University DuPont Best Undergraduate Award
    \end{tablist}

    \section*{Service}

    \begin{tablist}
        \item[2023--26] \tab{}Reviewer/PC: CHI, FAccT, EAAMO, DIS, IEEE S\&P, ACM TOMM
        \item[2024--] \tab{}Organizer, EAAMO Urban Data Science Working Group
        \item[2025] \tab{}Reviewer, Cornell CS PhD Admissions Committee
    \end{tablist}

    % display today's date as Month Year after a vertical space below the end of the text
    \begin{center}
        \vfill
        Updated \monthyeardate\today
    \end{center}

\end{document}
